### 2021-08-12 paper/paper.tex
Slightly rephrase conclusions to match new section on MPI parallelism

Based on our experience, we consider Julia to be suitable for simulation-focused
scientific computing, in particular for hyperbolic PDEs, computational fluid
dynamics, and related problems --- at least on the scale of shared memory
parallelism. The scalability of high-order methods for hyperbolic PDEs written
in Julia to high-performance computing applications still needs to be demonstrated.
However, we do not expect this to remain an unsolvable problem since Julia is not
generically slower than traditional compiled HPC programming languages. Nevertheless,
it appears to be more complicated to scale Julia to HPC while still keeping the
code as simple, clean, and flexible as it is now.

Learning a new programming language naturally requires some time and effort.
Nevertheless, it has paid off in our experience and we do not want to miss the
many useful features of \trixi enabled by Julia and its ecosystem. Thus, while there is
no need to switch to Julia if people are satisfied with their existing
tools, we encourage researchers to try out Julia and stay for a while. The Julia
community (on the Julia Discourse forum\footnote{\url{https://discourse.julialang.org}}
or Slack/Zulip workspaces) is usually welcoming and helpful, both for new and
experienced users. Making use of existing learning material and asking questions
appears to be important since a new programming style is necessary to make full
use of all of Julia's strengths.

>>>>

Based on our experience, we consider Julia to be suitable for simulation-focused
scientific computing, in particular for hyperbolic PDEs, computational fluid
dynamics, and related problems --- at least on the scale of shared memory
parallelism. The scalability of high-order methods for hyperbolic PDEs written
in Julia to high-performance computing applications still needs to be demonstrated.
Yet, we do not consider this an unsolvable problem, since Julia is not
generically slower than traditional compiled HPC programming languages. Nevertheless,
it appears to be more complicated to scale Julia to distributed systems without losing some of the
simplicity and flexibility it offers for serial or shared-memory parallel computations.

Learning a new programming language naturally requires some time and effort.
In our experience, however, it has paid off and we do not want to miss the
many useful features of \trixi enabled by Julia and its ecosystem. While there is
no need to switch to Julia if people are satisfied with their existing
tools, we encourage researchers to try out Julia for scientific computing and to stay for a while.
The Julia
community (on the Julia Discourse forum\footnote{\url{https://discourse.julialang.org}}
or Slack/Zulip workspaces) is usually welcoming and helpful, both for new and
experienced users. Making use of existing learning material and asking questions
appears to be important since a new programming style is necessary to make full
use of all of Julia's strengths.
